The K2 Halo Photometry Campaign

### 2019-03-27 paper/ms.tex
some updates

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass[modern]{aastex62}

@@

\author[0000-0001-8832-4488 ]{Daniel Huber}
\affiliation{Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

@@

% incorporation of k2sc
While the TV-min procedure produces in most cases a fairly clean light curve, there are nevertheless residual systematic errors related to spacecraft motion. In order to correct these, we employ the \texttt{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \texttt{POS\_CORR}) in pixels $(x,y)$. The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction in space evaluated for fixed time represents the pointing systematics and is subtracted from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science.

>>>>

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass[twocolumn]{aastex62}

@@

\author[0000-0001-8832-4488 ]{Daniel Huber}
\affiliation{Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

@@

% incorporation of k2sc
While the TV-min procedure produces in most cases a fairly clean light curve, there are nevertheless residual systematic errors related to spacecraft motion. In order to correct these, we employ the \textsc{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \textsc{pos\_corr}) in pixels $(x,y)$. The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction in space evaluated for fixed time represents the pointing systematics and is subtracted from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science. The target pixel files for C91, C92, and C101 include no position information, and there are no halo apertures for C112. As a result \textsc{k2sc}-corrected data are not available for these targets.
